\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\signature{Alexander Towell\\
Department of Computer Science\\
Southern Illinois University Edwardsville\\
Edwardsville, IL, USA\\
atowell@siue.edu\\
ORCID: 0000-0001-6443-9897}

\address{Alexander Towell\\
Department of Computer Science\\
Southern Illinois University Edwardsville\\
Edwardsville, IL 62026, USA}

\date{February 24, 2026}

\begin{document}

\begin{letter}{Editorial Board\\
PLOS Complex Systems\\
Special Issue: Complex Networks 2025}

\opening{Dear Editors,}

We are pleased to submit our manuscript, ``Temporal evolution of cognitive knowledge networks in AI-assisted conversations,'' by Alexander Towell and John Matta, for consideration in the PLOS Complex Systems special issue on Complex Networks 2025 (Submission ID: 41).

This manuscript extends our conference paper published in the Springer proceedings of Complex Networks 2025, ``Cognitive MRI of AI Conversations: Analyzing AI Interactions through Semantic Embedding Networks'' (Towell \& Matta, 2025). The conference paper introduced a methodology for transforming ChatGPT conversation archives into semantic similarity networks and analyzed the resulting static network structure.

The present journal extension adds substantial new material, constituting approximately 60\% new content beyond the conference paper. The core new contribution is a comprehensive temporal evolution analysis tracking the network's growth over 29 monthly snapshots. Specifically, we contribute:

\begin{itemize}
  \item Discovery of super-linear densification ($\gamma = 1.405$, $R^2 = 0.993$) following the same power-law form observed in citation and social networks.
  \item Empirical measurement of sub-linear preferential attachment ($\beta = 0.763$) with statistical validation via permutation testing.
  \item Community lifecycle tracking across 29 snapshots using Jaccard-based alignment, revealing 40 tracked communities with early stabilization.
  \item Bridge formation dynamics showing persistence of cross-domain connector conversations.
  \item Model era comparison revealing distinct topological signatures across LLM generations.
\end{itemize}

These findings demonstrate that individual AI-assisted knowledge exploration self-organizes according to the same macroscopic laws observed in collective knowledge systems---a result we believe fits well within the scope of this special issue on complex networks.

All data and code for reproducing the analyses are publicly available at \url{https://github.com/queelius/chatgpt-complex-net} (DOI: 10.5281/zenodo.15314235).

This manuscript has not been submitted elsewhere and is not under consideration at any other journal. All authors have approved the manuscript for submission.

\closing{Sincerely,}

\end{letter}
\end{document}
